Paper 1 Notebook

### 2023-11-30 minos/outcomes/paper_1_notebook.Rmd
updating future mice to full params

mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
mice.data$region <- factor(mice.data$region)

@@

load_cache <- F
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 20
  max_iter <- 5
  # future mice is parallelised version of MICE.
  mice_set <- futuremice(data = mice.data, #method=method,
                   #m = 10, maxit = 30,
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T)
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}

>>>>

@@

mice_columns <- c("age", 
                  "region", 
                  #"heating", 
                  "job_sec", 
                  "ncigs",
                  "education_state",            
                  "ethnicity",
                  "loneliness",
                  "sex", 
                  "SF_12",
                  #"SF_12p",
                  "smoker",
                  "nkids",       
                  "behind_on_bills",
                  "financial_situation",
                  "future_financial_situation",
                  "likely_move",
                  "ghq_depression",
                  "ghq_happiness",
                  "clinical_depression", 
                  "scsf1",
                  "health_limits_social",
                  #"hhsize",
                  #"housing_tenure",
                  #"urban", 
                  "housing_quality",
                  "hh_income",
                  "neighbourhood_safety",
                  "S7_labour_state",
                  #"yearly_energy",
                  "nutrition_quality"
                  #"hh_comp", 
                  #"marital_status"
)

mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
mice.data$region <- factor(mice.data$region)
mice.data$heating <- factor(mice.data$heating)
mice.data$job_sec <- factor(mice.data$job_sec)
mice.data$education_state <- factor(mice.data$education_state)
mice.data$sex <- factor(mice.data$sex)
mice.data$smoker <- factor(mice.data$smoker)
mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
mice.data$ghq_depression <- factor(mice.data$ghq_depression)
mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
mice.data$clinical_depression <- factor(mice.data$clinical_depression)
mice.data$scsf1 <- factor(mice.data$scsf1)
mice.data$health_limits_social <- factor(mice.data$ghq_depression)
mice.data$housing_tenure <- factor(mice.data$housing_tenure)
mice.data$urban <- factor(mice.data$urban)
mice.data$marital_status <- factor(mice.data$marital_status)

load_cache <- F
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 30
  max_iter <- 10
  ignore_cols = c("birth_year")
  # future mice is parallelised version of MICE.
  #mice_set <- mice(data = mice.data[, mice_columns], #method=method,
  #                 m = n_iter, maxit = max_iter,
  #                 remove.collinear=T)

  mice_set <- futuremice(data = mice.data[, imp_columns], #method=method,
                   m = n_iter, minit = max_iter,
                   remove.collinear=T, progressor = progressor)
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}
